Notes on the low density parameters in {\tt MAESTRO}

### 2009-06-05 docs/lo_density/lo_density.tex
add section reference for runtime_parameters
we compute cutoff using less than or equal to rather than less than

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
that particular cutoff value.  We set the coordinates at the following points in the
code:

@@

\section{anelastic\_cutoff}

@@

\section{base\_cutoff\_density}

>>>>

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value.  We set the coordinates at the following 
points in the code:

@@

\section{anelastic\_cutoff}\label{Sec:Anelastic Cutoff}

@@

\section{base\_cutoff\_density}\label{Sec:Base Cutoff Density}
